---
title: "Linear and Ridge Regressions"
author: "Torrin Danner, Nickolajs Prihodko, Joshua Hudson, Sascha Schmalz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The __linreg__ package is an alternative package to the lm package to make a linear regression. This document is not an introduction to linear regression. Furthermore it shall guide you to use the functions of the __linreg__ to perform a linear regression. The calculations are based on the `iris` dataset.

## Creating a Linreg object

Use the `linreg(formula, data)` function to create a `Linreg` object.

```{r, echo = FALSE, message = FALSE}
devtools::use_package("pryr")
```

```{r, results = 'hide'}
library(linreg)
data(iris)

tmp <- linreg(formula = Sepal.Length ~ Sepal.Width, data = iris)
pryr::otype(tmp)
```

The `Linreg` object will be of class `RC`. Using `otype()` out of the `pryr` package will return:
```{r}
pryr::otype(tmp)
```

The `Linreg` object is the starting point for the linear regression. It will allow you to perform several operations on the object.

## Operations on a Linreg object

The following functions are implemented:

| Function  | Description                                                               |
|-----------|---------------------------------------------------------------------------|
| print()   | prints the coefficients and the coeffienct names                          |
| resid()   | returns a vector of residuals $e$                                         |
| pred()    | returns predicted values $\hat{y}$                                        |
| coef()    | returns coefficients as a named vector                                    |
| summary() | returns the standard error, t-value, p-value, the estimate of $\hat{\sigma}$ and the degrees of freedom |
| plot()    | plots 'Residuals vs. Fitted' and 'Scale-Location' using `ggplot2`         |

In the following you will find a detailed description to each of the functions.

## How to call functions

In general a function is called by `tmp$functionname` where `tmp` is a `Linreg` object. In the following you will find an overview of all functions and the corresponding outpouts. 

The `print()` function will show you the specifications of the Linreg object, its coefficients and the name of its coefficients.

```{r}
tmp$print()
```

The `resid()` function will return a vector of the residuals of the linear regression model:
```{r}
residuals <- tmp$resid()
head(residuals, 10)
```

The `pred()` function will return a vector of the predicted values of the linear regression model:
```{r}
predicted <- tmp$pred()
head(predicted, 10)
```

The `coef()` function will return the coefficients of the linear regression model:
```{r}
tmp$coef()
```

The `summary()` function will return the standard error, t-value, p-value, the estimate of $\hat{\sigma}$ and the degrees of freedom of the linear regression model:
```{r}
tmp$summary()
```

The `plot()` function will plot the residuals vs. the fitted values as well as the scale location using `ggplot2`. (The `plot()` function requires the package `ggplot2`.)

```{r, echo = FALSE, message = FALSE}
devtools::use_package("ggplot2")
```

```{r, results = 'hide', message = FALSE, fig.width = 5}
tmp$plot()
```

## Creating a Ridgereg object
The only difference from `linreg` is that there is one more mandatory parameter `lambda`.
```{r, results = 'hide', tidy = TRUE}
tmp <- ridgereg(formula = Sepal.Length ~ Sepal.Width + Petal.Length, data = iris, lambda = 0)
```

The functionality of the returned `Ridgereg` object is also very similar to `linreg`:

| Function  | Description                                                               |
|-----------|---------------------------------------------------------------------------|
| print()   | prints the coefficients and the coeffienct names                          |
| resid()   | returns a vector of residuals $e$                                         |
| pred()    | returns predicted values $\hat{y}$                                        |
| coef()    | returns coefficients as a named vector                                    |
| plot()    | plots 'Residuals vs. Fitted' and 'Scale-Location' using `ggplot2`         |

For example
```{r}
tmp$coef()
````

```{r, results = 'hide', message = FALSE, fig.width = 5}
tmp$plot()
```

